Smart Representations: {R}ationality and Evolution in a Richer Environment

### 2016-09-23 paper/PoS_paper_final.tex
Final version

\usepackage{geometry}
 % \geometry{
 % a4paper,
 % left=300mm,
 % right=250mm,
 % top=400mm,
 % bottom=400mm
 % }

@@

% paper size, margins, etc:
\usepackage{geometry}
\geometry{verbose,letterpaper,tmargin=1.5in,bmargin=1.5in,lmargin=1.25in,rmargin=1in}

@@

\begin{document}

\maketitle

@@

@@

If agents deal with a rich and variable environment, they have to face many different choice
situations.  Standard evolutionary game models frequently simplify reality in at least two
ways. Firstly, the environment is represented as a fixed \emph{stage game}; secondly, the focus
of evolutionary selection is behavior for that stage game alone. In contrast, some argue for
studying the evolutionary competition of general \emph{choice mechanisms} in a rich and
variable environment
\citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche,HammStev12}. In
response to this and adding to recent like-minded approaches, this paper introduces a general
\emph{meta-game} model that conservatively extends the scope of evolutionary game theory to
deal with evolutionary selection of choice mechanisms in variable environments \citep[see
also][]{Harley1981:Learning-the-Ev,ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o,OConnor2016:Evolving-to-Gen,RayoBecker07,Zollman2008,SkyrmsZollman10,BednarPage07}.\footnote{Some
  of these contributions are very closely related to ours. \citet{BednarPage07} use a
  multi-game framework, composed of a fixed selection of six possible games, to study the
  emergence of different cultural behaviors, and model agents as finite-state automata playing
  games from the fixed selection. \citet{Zollman2008} explains seemingly ``irrational'' fair
  behavior in social dilemmas (like the Ultimatum game) by means of a model where agents have
  to play the Ultimatum game together with the Nash bargaining game, but they are constrained
  to choose the same strategy for both games. Finally, \citet{RayoBecker07} consider, in a more
  decision-theoretic setting, what subjective utility function a cognitively limited agent
  should be endowed with in order to maximize her evolutionary fitness. Our framework can then
  be viewed as a generalization of those models, mainly in that here players do not necessarily
  have any specific cognitive limitations, and we allow for larger and possibly variable
  classes of games.}

@@

Going beyond a single fixed fitness game, we consider a \textit{class} of possible games. For
concreteness, let $\mathcal{G}$ be a class of two-player symmetric games, together with a
probability measure $P_{\mathcal{G}}(G)$ for the occurrence probability of game
$G \in \mathcal{G}$. Intuitively, the probability $P_{\mathcal{G}}$ encodes the statistical
properties of the environment. A \textit{meta-game} is then a tuple
$ MG=\langle CM, \mathcal{G}, P_{\mathcal{G}},F \rangle$, where $CM$ is a set of choice
mechanisms, $\mathcal{G}$ is a class of possible games, $P_{\mathcal{G}}(G)$ is the probability
of game $G$ to occur, and $F:CM \times CM \rightarrow \mathbb{R}$ is the (meta-)fitness
function, defined as:
\begin{align}
  \label{eq:FittnessChoiceMechGamePairwise}
  F(c, c') = \int P_{\mathcal{G}}(G) \  F_G(c,c') \text{ d} G \,.
\end{align}
Hence, $F(c,c')$ determines the evolutionary payoff of choice mechanism $c$ against $c'$ in the
meta-game. The set $CM$ can be thought of as the set of choice mechanisms that are present within a given
population playing the games from the class $\mathcal{G}$. Consequently, it is possible
to compute the average fitness of $c$ against the population, that is given by:
\begin{align}
  \label{eq:FittnessChoiceMechGame}
  F(c) = \int P_{M}(c') \ F(c,c') \text{ d} c' = \int \int P_{\mathcal{G}}(G) \  P_{M}(c') \  F_G(c,c') \text{ d} c' \text{ d} G  \,,
\end{align}
where $P_{M}(c')$ is the probability of
encountering a co-player with choice mechanism $c'$.

@@

Although a thorough discussion of this issue goes beyond the scope of this work, let us say
that these two kinds of belief underlie two different and alternative views on
uncertainty. Faced with uncertain events, a strict Bayesian will always form a precise belief,
specified by a \textit{single} probability $\mu$. In the absence of any information about
future uncertain events, the Bayesian would mostly invoke the \textit{principle of insufficient
  reason}, and accordingly choose a uniform probability over the possible outcomes. In
contrast, others have argued against the obligation of representing a belief by means of a
single probability measure, opposite to the Bayesian paradigm (e.g., \cite{GilbMarin13}). They
argue instead in favor of a more encompassing account, according to which uncertainty can be
\emph{unmeasurable}, and represented by a (convex and compact) set of probabilities (e.g.,
\cite{gilsch89}). This line of thought has its origin in decision theory, motivated by
Ellsberg's famous paradoxes \citep{ells61}, and appears extremely relevant in game-theoretic
contexts too. Indeed, in a recent paper \citet{BattCerrMM15} write:

\begin{quote}
  Such [unmeasurable] uncertainty is inherent in situations of strategic interaction. This is quite obvious
  when such situations have been faced only a few times. (p.~646)
\end{quote}

\noindent In evolutionary game theory, for instance, players obviously face uncertainty
about the composition of the population that they are part of, and consequently about the (type of)
co-player that they are randomly paired with at each round and about the co-player's action. In
case of complete lack of information about the composition of the population, a non-Bayesian player would thus entertain maximal
unmeasurable uncertainty, i.e., a maximally imprecise belief.\footnote{Such a radical
  uncertainty could ensue, for example, if agents have no conception of their co-player or her
  preferences. Unsophisticated agents, as considered in evolutionary game theory, might be
  entirely unaware of the fact that they are engaged in social decision making (see \cite{HeifetzMeier2009:Dynamic-Unaware}, for
  game-theoretic models of unawareness). It is therefore
  not ludicrous to consider radical uncertainty first and tend to more
  sophisticated ways of forming beliefs later (more on this below).} As already anticipated, we
will see that the way agents form beliefs, and the possibility of holding imprecise beliefs
in particular, can have a fundamental impact on their evolutionary success.

@@

As observed earlier, meta-games factor in statistical properties of the environment. For particular
empirical purposes, one could consult a specific class of games $\mathcal{G}$ with appropriate,
maybe empirically informed probability $P_{\mathcal{G}}$ in order to match the natural
environment of a given population. For our present purposes, let $\mathcal{G}$ be a set of symmetric
two-player fitness games with two acts for a start. Each game $G \in \mathcal{G}$ is then individuated solely by its payoff
function, i.e., by a quadruple of numbers $G=(a,b,c,d)$. As for the occurrence probability
$P_{\mathcal{G}}(G)$ of game $G$, we imagine that the values $a,b,c,d$ are i.i.d.~random
variables sampled from the set $ \lbrace 0, \dots, 10 \rbrace$ according to uniform probability
$P_{V}$. Using Monte Carlo simulations, we can then approximate the values of
equation~(\ref{eq:FittnessChoiceMechGamePairwise}) to construct meta-game payoffs. Results
based on $100.000$ randomly sampled games are given in
table~\ref{tab:ExpectedFitness_4Types}.\footnote{Concretely, $100.000$ games were sampled
  repeatedly by choosing independently four integers between 0 and 10 uniformly at random. For
  each game, the action choices of all four choice mechanisms were determined and payoffs from
  all pairwise encounters recorded. The number in each cell of
  table~\ref{tab:ExpectedFitness_4Types} is the average payoff for the choice mechanism listed
  in the row when matched with the choice mechanism in the column.}

@@

This result presupposes at least occasional imprecise beliefs. The assumed imprecise beliefs do not need to be maximally uncertain, however.  Let
the uncertainty held by a player be defined by a convex compact set of probabilities
$ [s,t] \subseteq \Delta(A) $ over the co-player's actions, where $s$ is the lower probability
and $t$ is the upper probability of action $II$.  We can then prove the following proposition,
which is the analogue of Proposition~\ref{proposition1} for any possible (not necessarily
maximal) degree of uncertainty $[s,t]$, with $s \neq t$. There is only one difference: we are
now going to require i.i.d. drawing of a \emph{continuous} random variable. This is due to the
fact that, for arbitrarily small intervals $[s,t]$, objective players $([s,t],\text{obj})$ and
regret players $([s,t],\text{reg})$ can behave as holding a unique probability measure (precise
belief) if the underlying payoff space is not dense. The reason for this technical requirement
will become clearer from the proof.

\begin{proposition} \label{proposition2} In the class of $2\times2$ symmetric games generated
  by i.i.d. drawing of a continuous random variable from a distribution with density $P_V$ and
  support $(\underline{r},\overline{r}) \subseteq \mathbb{R}$, for any imprecise
  belief $[s,t]$, the only evolutionarily stable state of a population with regret players
  $([s,t],\text{reg})$ and objective players $([s,t],\text{obj})$ is a monomorphic state of
  $([s,t],\text{reg})$ players.
\end{proposition}

@@

The space of possible preference types is enormous, and we have only compared regret
and objective types so far. Let us now
look at two other types of subjective preferences that have been investigated, especially
in behavioral economics and in evolutionary game theory. A famous example is the
\textit{altruistic} preference \citep[e.g.,][]{Beck76,BestGuth98}, summoned to explain the
possibility of altruistic behavior. At the other end of the spectrum, the \emph{competitive}
preference is located. The two subjective utilities are defined as follows:
\begin{enumerate}
\item \textit{altruistic} utility: for all $G \in \mathcal{G}$, $\text{alt}^G(a,a') = \pi^G(a,a') + \pi^G(a',a)$;\footnote{A
    more general formulation would be to define $ \alpha$-altruistic utility, for
    $\alpha \in [0,1]$,
    $ u^G_\alpha(a, a')=\pi^G(a,a') + \alpha \pi^G(a',a)$. Since we are not
    interested in the evolution of degrees of altruism, here we simply fix $ \alpha = 1 $. Analogously for $\alpha$-competitive utilities too.}
\item \textit{competitive} utility: for all $G \in \mathcal{G}$, $\text{com}^G(a,a') = \pi^G(a,a') - \pi^G(a',a)$.
\end{enumerate}

@@

To see how different choice mechanisms behave in evolutionary competition based on solitary
decision making, we approximated, much in the spirit of meta-games, average accumulated
fitness obtained in randomly generated solitary decision problems. For our purposes, a decision
problem $D=\tuple{W, \Acts, \pi^D}$ consists of a set of states of the world $W$, a set of acts $\Acts$, and
a payoff function $\pi^D: W \times \Acts \rightarrow \mathbb{R}$.  We generate arbitrary
decision problems by selecting, uniformly at random, numbers of states and acts
$n^{D}_w, n^{D}_\act \in \set{2, \dots, 10}$ and then filling the payoff table, so to speak, by
i.i.d.~samples for each $\pi^D(w, \act) \in \set{0, 10}$. Unlike with
two-player games, we need to also sample the actual state of the world, which we selected
uniformly at random from the available states in the current decision problem. Accordingly, the fitness of choice mechanism $c$ in decision problem $D$ is given by:
$$F_D(c)= \pi^D(w,a_c^*(u_c^D,\Gamma_c))\overline{\mu}(w),$$ with $ \overline{\mu}(w)= \frac{1}{n_w^D}$ for all $w$.
As subjective representations,
we considered the original cast of four from table~\ref{tab:ExpectedFitness_4Types}, since altruistic and
competitive types are meaningless in solitary decision situations. As before, the
relevant fitness measure, defined in equation~(\ref{eq:FittnessChoiceMechSolitary}), was
approximated by Monte Carlo simulations, the results of which are given in
table~\ref{tab:SolitaryDecisions}.
\begin{align}
  \label{eq:FittnessChoiceMechSolitary}
  F(c) = \int P_{\mathcal{D}}(D) \  F_D(c) \text{ d} D 
\end{align}
\begin{table}
  \centering
  \begin{tabular}{cccc}
    \toprule
   $(\text{reg}, \text{imp})$ 
 & $(\text{obj}, \text{imp})$ 
 & $(\text{reg}, \text{prc})$ 
 & $(\text{obj}, \text{prc})$ 
 \\ \midrule
    6.318 & 6.237 & 6.661 & 6.661 \\ \bottomrule
  \end{tabular}
  \caption{Expected fitness of choice mechanisms approximated from 100.000 simulated solitary
    decision problems (see main text).}
  \label{tab:SolitaryDecisions}
\end{table}
Facts~\ref{fact:maxEU-minReg} and \ref{fact:equivalence2x2} still apply:
$(\text{reg}, \text{prc})$ and $(\text{obj}, \text{prc})$ are behaviorally equivalent in
general, and $(\text{reg}, \text{imp})$ is behaviorally equivalent to the former two in
decision problems with two states and two acts. This shows in the results from
table~\ref{tab:SolitaryDecisions} in that the averages for $(\text{reg}, \text{prc})$ and
$(\text{obj}, \text{prc})$ are identical. But since we included decision problems with more
acts and more states as well, the average for regret minimizers $(\text{reg}, \text{imp})$ is
not identical to the one of $(\text{reg}, \text{prc})$ and $(\text{obj}, \text{prc})$. It
is, in fact, lower, but again not as low as that of $(\text{obj}, \text{imp})$.

@@

The assumption that players and decision makers maximize their (subjective) utility is central
through in the economics literature, and the maximization of actual (objective) payoffs is
often justified by appealing to evolutionary arguments and natural selection. In contrast to
the standard view, we showed the existence of player types with subjective utilities different
from the actual evolutionary payoffs that can outperform types whose subjective utilities
coincide with the evolutionary payoffs. The claim is not that regret preferences are the best
on the market, but rather that utilities that perfectly mirror evolutionary fitness can be
outclassed by subjective utilities that differ from the objective fitness.  While the
literature on evolution of preferences has focused on fixed games, we have adopted a more
general approach here. We suggested that attention to “meta-games” is crucial, because what may
be a good subjective representation in one type of game (e.g., cooperative preferences in the
Prisoner’s Dilemma class) need not be generally beneficial. Taken together, we presented a
variety of plausible circumstances in which evolutionary competition between choice mechanisms
on a larger class of games can favor non-veridical preference representations focusing on
regret.

@@

  & \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})) + b_{C} \cdot
  (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC})) \\ 
  & \ \ + c_{C} \cdot (P(II_{RC}\cap I_{RC})
  +P(II_{RC}\cap II_{RC})) + d_{C} \cdot (P(II_{RC}\cap II_{RC})+P(II_{RC}\cap I_{RC}))] \\
  > & 
  \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot P(I_{RC}\cap I_{MC}) + b_{C} \cdot P(I_{RC}\cap I_{MC}) +
  c_{C} \cdot (P(I_{RC}\cap II_{MC})+P(II_{RC}\cap II_{MC})) \\ 
Rewrite:

@@

\begin{align*} 
& \textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (P(I_{RC}\cap I_{RC}) + P(I_{RC}\cap II_{RC})) + b_{C} \cdot  (P(I_{RC}\cap II_{RC}) + P(I_{RC}\cap I_{RC}))\\
& \ \ \ \ + c_{C} \cdot (P(II_{RC}\cap I_{RC}) +P(II_{RC}\cap II_{RC})- P(I_{RC}\cap II_{MC})- P(II_{RC}\cap II_{MC}))\\
& \ \ \ \ + d_{C} \cdot (P(II_{RC}\cap II_{RC})+P(II_{RC}\cap I_{RC})- P(II_{RC}\cap II_{MC})- P(I_{RC}\cap II_{MC}))]> 0
\end{align*}
that is
\begin{align*}
\textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (\frac{1}{4}+\frac{1}{4}) + b_{C} \cdot  (\frac{1}{4}+\frac{1}{4}) + c_{C} \cdot (\frac{1}{4}+\frac{1}{4}-\frac{1}{2}-\frac{1}{2}) + d_{C} \cdot (\frac{1}{4}+\frac{1}{4}-\frac{1}{2}-\frac{1}{2})]> 0
\end{align*}
%\begin{align*}
%\textstyle{\sum_{C_{a>d}}} P(C)[\frac{1}{2}a_{C}+ \frac{1}{2}b_{C} - \frac{1}{2}c_{C} - \frac{1}{2}d_{C}]> 0
%\end{align*}
\noindent Since we have assumed $ a-c = d-b $, the last inequality is not satisfied. We have instead:

@@

\end{itemize}
\noindent Finally, we can conclude that
$F_{\mathcal{C}\cup\mathcal{A}}(M,M)<F_{\mathcal{C}\cup\mathcal{A}}(R,M)$. As before, notice
that, when we have i.i.d. sampling with continuous support, games in $\mathcal{W}$ and
$\mathcal{B}$ never occur, but the proof is the same for all the other cases. Hence, both when
the support of $a,b,c,d$ is finite, and when the support is infinite, $R$ strictly dominates
$M$ under the conditions assumed. \hfill $\dashv$

@@

%
\node (zero) [] at (-.75,-.5) {$P(II)=0$};

%
\node (s) [] at (2,0)
  [label=below:{$s$}] {|};
%
\node (t) [] at (4,0)
  [label=below:{$t$}] {|};
%
%\node (st) [] at (3,0)
 % [label=below:{$s + \nicefrac{\epsilon}{2}$}] {};

\draw [dashed] (2,0) -- (2,5);
\draw [dashed] (4,0) -- (4,5);

\draw [dotted] (3,0) -- (3,5);

%
\node (a') [] at (1.8,2.6)
  [label=left:{}] {$a'$};
\node (c') [] at (2.2,2)
  [label=left:{}] {$c'$};
\node (d') [] at (4.2,4)
  [label=left:{}] {$d'$};
\node (b') [] at (4.2,2.6)
  [label=left:{}] {$b'$};

%
\node (0y) [] at (0,0)
  [label=left:{$c$}] {};
\node (1y) [] at (0,1)
  [label=left:{}] {-};
\node (2y) [] at (0,2)
  [label=above right:{$I$}] [label=left:{$a$}] {-};

>>>>

%\usepackage{geometry}
 % \geometry{
 % a4paper,
 % left=300mm,
 % right=250mm,
 % top=400mm,
 % bottom=400mm
 % }

@@

% paper size, margins, etc:
\usepackage[top=4cm, bottom=4cm, left=3cm, right=2.5cm]{geometry}
%\geometry{verbose,letterpaper,tmargin=1.5in,bmargin=1.5in,lmargin=1.25in,rmargin=1in}

@@

\title{Smart Representations: {R}ationality and Evolution in a Richer  Environment}
\author{Paolo Galeazzi $^{1}$ and Michael Franke $^{2}$\\
{\footnotesize
$^{1}$ ILLC, University of Amsterdam, The Netherlands; email: pagale87@gmail.com}\\
{\footnotesize
$^{2}$ Department of Linguistics, University of T\"{u}bingen, Germany; email: mchfranke@gmail.com}
}
\date{}

\begin{document}
\begin{titlepage}
\maketitle

@@

\footnotetext{The research of Paolo Galeazzi leading to these results
  has received funding from the European Research Council under the
  European Community’s Seventh Framework Programme (FP7/2007-2013)/ERC
  Grant agreement No. 283963. Michael Franke’s work was supported by
  the Institutional Strategy of the University of T\"{u}bingen (DFG,
  ZUK 63). The authors are also grateful to Gerhard J{\"a}ger for
  funding this work. We want to thank all the participants in
  Decisions, Games and Logic ’15 workshop at London School of
  Economics, in LogiCIC workshop 2014 at the University of Amsterdam,
  and in Bridges 2 workshop at Rutgers University for the valuable
  feedback. Special thanks go to Pierpaolo Battigalli, Massimo
  Marinacci, Valerio Nispi Landi, Tommaso Orlando, Eric Pacuit, Erik
  Quaeghebeur, Rasmus Rendsvig, Teddy Seidenfeld, Peter Wakker, and
  Kevin Zollman for their attention and comments. We are also grateful
for the helpful comments we received by two anonymous reviewers.}

\end{titlepage}

@@

If agents deal with a rich and variable environment, they have to face many different choice
situations.  Standard evolutionary game models frequently simplify reality in at least two
ways. Firstly, the environment is represented as a fixed \emph{stage game}; secondly, the focus
of evolutionary selection is behavior for that stage game alone. In contrast, some argue for
studying the evolutionary competition of general \emph{choice mechanisms} in a rich and
variable environment
\citep[e.g.,][]{FawcettHamblin2013:Exposing-the-be,McNamara2013:Towards-a-Riche,HammStev12}. In
response to this and adding to recent like-minded approaches, this paper introduces a general
\emph{meta-game} model that conservatively extends the scope of evolutionary game theory to
deal with evolutionary selection of choice mechanisms in variable environments \citep[see
also][]{Harley1981:Learning-the-Ev,ZollmanSmead2010:Plasticity-and-,SmeadZollman2013:The-Stability-o,OConnor2016:Evolving-to-Gen,RayoBecker07,Zollman2008,SkyrmsZollman10,BednarPage07}.\footnote{Some
  of these contributions are closely related to ours. \citet{BednarPage07} use a
  multi-game framework, composed of a fixed selection of six possible games, to study the
  emergence of different cultural behaviors, and model agents as finite-state automata playing
  games from the fixed selection. \citet{Zollman2008} explains seemingly ``irrational'' fair
  behavior in social dilemmas (like the Ultimatum game) by means of a model where agents have
  to play the Ultimatum game together with the Nash bargaining game, but they are constrained
  to choose the same strategy for both games. Finally, \citet{RayoBecker07} consider, in a more
  decision-theoretic setting, what subjective utility function a cognitively limited agent
  should be endowed with in order to maximize her evolutionary fitness. Our framework can then
  be viewed as a generalization of those models, mainly in that here players do not necessarily
  have any specific cognitive limitations, and we allow for larger and possibly variable
  classes of games.}

@@

Going beyond a single fixed fitness game, we consider a \textit{class} of possible games. For
concreteness, let $\mathcal{G}$ be a class of two-player symmetric games, together with a
probability measure $P_G(G')$ for the occurrence probability of game
$G' \in \mathcal{G}$. Intuitively, the probability $P_G$ encodes the statistical
properties of the environment. A \textit{meta-game} is then a tuple
$ MG=\langle CM, \mathcal{G}, P_G,F \rangle$, where $CM$ is a set of choice
mechanisms, $\mathcal{G}$ is a class of possible games, $P_G(G')$ is the probability
of game $G'$ to occur, and $F:CM \times CM \rightarrow \mathbb{R}$ is the (meta-)fitness
function, defined as:
\begin{align}
  \label{eq:FittnessChoiceMechGamePairwise}
  F(c, c') = \int  F_G(c,c') \text{ d} P_G(G) \,.
\end{align}
Hence, $F(c,c')$ determines the evolutionary payoff of choice mechanism $c$ against $c'$ in the
meta-game. The set $CM$ can be thought of as the set of choice mechanisms that are present within a given
population playing the games from the class $\mathcal{G}$. Consequently, it is possible
to compute the average fitness of $c$ against the population, that is given by:
\begin{align}
  \label{eq:FittnessChoiceMechGame}
  F(c) = \int F(c,c') \text{ d} P_{c}(c') = \int \int   F_G(c,c') \text{ d} P_c(c') \text{ d} P_G(G)  \,,
\end{align}
where $P_c(c')$ is the probability of
encountering a co-player with choice mechanism $c'$.

@@

Although a thorough discussion of this issue goes beyond the scope of this work, let us say
that these two kinds of belief underlie two different and alternative views on
uncertainty. Faced with uncertain events, a strict Bayesian will always form a precise belief,
specified by a \textit{single} probability $\mu$. In the absence of any information about
future uncertain events, the Bayesian would mostly invoke the \textit{principle of insufficient
  reason}, and accordingly choose a uniform probability over the possible outcomes. In
contrast, others have argued against the obligation of representing a belief by means of a
single probability measure, opposite to the Bayesian paradigm (e.g., \cite{GilbMarin13}). They
argue instead in favor of a more encompassing account, according to which uncertainty can be
\emph{unmeasurable}, and represented by a (convex and compact) set of probabilities (e.g.,
\cite{gilsch89}). This line of thought has its origin in decision theory, motivated by
Ellsberg's famous paradoxes \citep{ells61}, and appears extremely relevant in game-theoretic
contexts too. Indeed, in a recent paper \citet{BattCerrMM15} write: ``Such [unmeasurable] uncertainty is inherent in situations of strategic interaction. This is quite obvious
  when such situations have been faced only a few times.''

In evolutionary game theory, for instance, players obviously face uncertainty
about the composition of the population that they are part of, and consequently about the (type of)
co-player that they are randomly paired with at each round and about the co-player's action. In
case of complete lack of information about the composition of the population, a non-Bayesian player would thus entertain maximal
unmeasurable uncertainty, i.e., a maximally imprecise belief.\footnote{Such a radical
  uncertainty could ensue, for example, if agents have no conception of their co-player or her
  preferences. Unsophisticated agents, as considered in evolutionary game theory, might be
  entirely unaware of the fact that they are engaged in social decision making (see \cite{HeifetzMeier2009:Dynamic-Unaware}, for
  game-theoretic models of unawareness). It is therefore
  not ludicrous to consider radical uncertainty first and tend to more
  sophisticated ways of forming beliefs later (more on this below).} As already anticipated, we
will see that the way agents form beliefs, and the possibility of holding imprecise beliefs
in particular, can have a fundamental impact on their evolutionary success.

@@

As observed earlier, meta-games factor in statistical properties of the environment. For particular
empirical purposes, one could consult a specific class of games $\mathcal{G}$ with appropriate,
maybe empirically informed probability $P_G$ in order to match the natural
environment of a given population. For our present purposes, let $\mathcal{G}$ be a set of symmetric
two-player fitness games with two acts for a start. Each game $G \in \mathcal{G}$ is then individuated solely by its payoff
function, i.e., by a quadruple of numbers $G=(a,b,c,d)$. As for the occurrence probability
$P_G(G)$ of game $G$, we imagine that the values $a,b,c,d$ are i.i.d.~random
variables sampled from the set $ \lbrace 0, \dots, 10 \rbrace$ according to uniform probability
$P_{V}$. Using Monte Carlo simulations, we can then approximate the values of
equation~(\ref{eq:FittnessChoiceMechGamePairwise}) to construct meta-game payoffs. Results
based on $100.000$ randomly sampled games are given in
table~\ref{tab:ExpectedFitness_4Types}.\footnote{Concretely, $100.000$ games were sampled
  repeatedly by choosing independently four integers between 0 and 10 uniformly at random. For
  each game, the action choices of all four choice mechanisms were determined and payoffs from
  all pairwise encounters recorded. The number in each cell of
  table~\ref{tab:ExpectedFitness_4Types} is the average payoff for the choice mechanism listed
  in the row when matched with the choice mechanism in the column.}

@@

This result presupposes at least occasional imprecise beliefs. The assumed imprecise beliefs do not need to be maximally uncertain, however.  Let
the uncertainty held by a player be defined by a convex compact set of probabilities
$ [s,t] \subseteq \Delta(A) $ over the co-player's actions, where $s$ is the lower probability
and $t$ is the upper probability of action $II$.  We can then prove the following proposition,
which is the analogue of Proposition~\ref{proposition1} for any possible (not necessarily
maximal) degree of uncertainty $[s,t]$, with $s \neq t$. There is only one difference: we are
now going to require i.i.d. drawing of a \emph{continuous} random variable with uniform distribution. This is due to the
fact that, for arbitrarily small intervals $[s,t]$, objective players $(\text{obj},[s,t])$ and
regret players $(\text{reg},[s,t])$ can behave as holding a unique probability measure (precise
belief) if the underlying payoff space is not dense. The reason for this technical requirement
will become clearer from the proof.

\begin{proposition} \label{proposition2} Let $\mathcal{G}$ be the class of symmetric $2\times2$ games generated
  by i.i.d. drawing of a continuous random variable with uniform distribution over any set of values, and fix any imprecise
  belief $[s,t]$. Then the only evolutionarily stable state of a population with regret players
  $(\text{reg},[s,t])$ and objective players $(\text{obj},[s,t])$ is a monomorphic state of
  $(\text{reg},[s,t])$ players.
\end{proposition}

@@

The space of possible preference types is enormous, and we have only compared regret
and objective types so far. Let us now
look at two other types of subjective preferences that have been investigated, especially
in behavioral economics and in evolutionary game theory. A famous example is the
\textit{altruistic} preference \citep[e.g.,][]{Beck76,BestGuth98}, summoned to explain the
possibility of altruistic behavior. At the other end of the spectrum, the \emph{competitive}
preference is located. The two subjective utilities are defined as follows:
\begin{enumerate}
\item \textit{altruistic} utility: for all $G \in \mathcal{G}$, $\text{alt}^G(a,a') = \pi^G(a,a') + \pi^G(a',a)$;
\item \textit{competitive} utility: for all $G \in \mathcal{G}$, $\text{com}^G(a,a') = \pi^G(a,a') - \pi^G(a',a)$.\footnote{A
    more general formulation would be to define $ \alpha$-altruistic utility, for
    $\alpha \in [0,1]$,
    $ u^G_\alpha(a, a')=\pi^G(a,a') + \alpha \pi^G(a',a)$. Since we are not
    interested in the evolution of degrees of altruism, here we simply fix $ \alpha = 1 $. Analogously for $\alpha$-competitive utilities too. Other possible generalizations could also take into account combinations of all these preferences with different decision rules. Maximax, minimax and minimin, for example, would be possible rules for choice. Here we opted for maxmin because we were specifically interested in comparing maxmin and regret minimization, as these are two major alternatives for decision making.}
\end{enumerate}

@@

To see how different choice mechanisms behave in evolutionary competition based on solitary
decision making, we approximated, much in the spirit of meta-games, average accumulated
fitness obtained in randomly generated solitary decision problems. For our purposes, a decision
problem $D=\tuple{W, \Acts, \pi^D}$ consists of a set of states of the world $W$, a set of acts $\Acts$, and
a payoff function $\pi^D: W \times \Acts \rightarrow \mathbb{R}$.  We generate arbitrary
decision problems by selecting, uniformly at random, numbers of states and acts
$n^{D}_w, n^{D}_\act \in \set{2, \dots, 10}$ and then filling the payoff table, so to speak, by
i.i.d.~samples for each $\pi^D(w, \act) \in \set{0, 10}$. Unlike with
two-player games, we need to also sample the actual state of the world, which we selected
uniformly at random from the available states in the current decision problem. Accordingly, the fitness of choice mechanism $c$ in decision problem $D$ is given by:
$$F_D(c)= \pi^D(w,a_c^*(u_c^D,\Gamma_c))\overline{\mu}(w),$$ with $ \overline{\mu}(w)= \frac{1}{n_w^D}$ for all $w$.
As subjective representations,
we considered the original cast of four from table~\ref{tab:ExpectedFitness_4Types}, since altruistic and
competitive types are meaningless in solitary decision situations. As before, the
relevant fitness measure, defined in equation~(\ref{eq:FittnessChoiceMechSolitary}), was
approximated by Monte Carlo simulations, the results of which are given in
table~\ref{tab:SolitaryDecisions}.
\begin{align}
  \label{eq:FittnessChoiceMechSolitary}
  F(c) = \int  F_D(c) \text{ d} P_{D}(D) 
\end{align}
\begin{table}
  \centering
  \begin{tabular}{cccc}
    \toprule
   $(\text{reg}, \text{imp})$ 
 & $(\text{obj}, \text{imp})$ 
 & $(\text{reg}, \text{prc})$ 
 & $(\text{obj}, \text{prc})$ 
 \\ \midrule
    6.318 & 6.237 & 6.661 & 6.661 \\ \bottomrule
  \end{tabular}
  \caption{Expected fitness of choice mechanisms approximated from 100.000 simulated solitary
    decision problems (see main text).}
  \label{tab:SolitaryDecisions}
\end{table}
Facts~\ref{fact:maxEU-minReg} and \ref{fact:equivalence2x2} still apply:
$(\text{reg}, \text{prc})$ and $(\text{obj}, \text{prc})$ are behaviorally equivalent in
general, and $(\text{reg}, \text{imp})$ is behaviorally equivalent to the former two in
decision problems with two states and two acts. This shows in the results from
table~\ref{tab:SolitaryDecisions} in that the averages for $(\text{reg}, \text{prc})$ and
$(\text{obj}, \text{prc})$ are identical. But since we included decision problems with more
acts and more states as well, the average for regret minimizers $(\text{reg}, \text{imp})$ is
not identical to the one of $(\text{reg}, \text{prc})$ and $(\text{obj}, \text{prc})$. It
is, in fact, lower, but again not as low as that of $(\text{obj}, \text{imp})$.

@@

The assumption that players and decision makers maximize their (subjective) utility is
central through all economic literature, and the maximization of actual (objective) payoffs is
often justified by appealing to evolutionary arguments and natural selection. In contrast to
the standard view, we showed the existence of player types with subjective utilities different
from the actual evolutionary payoffs that can outperform types whose subjective utilities
coincide with the evolutionary payoffs. Here the claim is not that regret preferences are the best on the market, but rather that utilities that perfectly mirror evolutionary fitness can be outclassed by subjective utilities that differ from the objective fitness.  While the literature on evolution of preferences has
focused on fixed games, we have adopted a more general approach here. We suggested that
attention to “meta-games” is crucial, because what may be a good subjective representation in
one type of game (e.g., cooperative preferences in the Prisoner’s Dilemma) need not be
generally beneficial. 
%Taken together, we presented a variety of plausible circumstances in which evolutionary competition between choice mechanisms on a larger class of games can favor non-veridical preference representations focusing on regret.

@@

@@

\begin{align*}
\textstyle{\sum_{C_{a>d}}} P(C)[a_{C} \cdot (\frac{1}{4}+\frac{1}{4}) + b_{C} \cdot  (\frac{1}{4}+\frac{1}{4}) + c_{C} \cdot (\frac{1}{4}+\frac{1}{4}-\frac{1}{2}-\frac{1}{2}) + d_{C} \cdot (\frac{1}{4}+\frac{1}{4}-\frac{1}{2}-\frac{1}{2})]> 0
\end{align*}
%\begin{align*}
%\textstyle{\sum_{C_{a>d}}} P(C)[\frac{1}{2}a_{C}+ \frac{1}{2}b_{C} - \frac{1}{2}c_{C} - \frac{1}{2}d_{C}]> 0
%\end{align*}
\noindent Since we have assumed $ a-c = d-b $, the last inequality is not satisfied. We have instead:

@@

\end{itemize}
\noindent Finally, we can conclude that
$F_{\mathcal{C}\cup\mathcal{A}}(M,M)<F_{\mathcal{C}\cup\mathcal{A}}(R,M)$.

When we have i.i.d. sampling with continuous support, games in $\mathcal{W}$ and
$\mathcal{B}$ never occur, and the proof for the other cases reduces to the proof of Proposition \ref{proposition2} for $s=0$ and $t=1$. \hfill $\dashv$

@@

%
\node (zero) [] at (-.95,-.5) {$P(II)=0$};

%
%\node (s) [] at (1,0)[label=below:{$s$}] {|};
%
\node (s) [] at (1.5,0)
  [label=below:{$\frac{3s+t}{4}$}] {|};
%
%\node (t) [] at (3,0) [label=below:{$\overline{\lambda}$}] {|};
%
%\node (st) [] at (3,0)
 % [label=below:{$s + \nicefrac{\epsilon}{2}$}] {};

\draw [dashed] (1,0) -- (1,5);
\draw [dashed] (3,0) -- (3,5);

\draw [dotted] (2,0) -- (2,5);

%
\node (0y) [] at (0,0)
  [label=left:{}] {};
\node (1y) [] at (0,1)
  [label=left:{}] {$\bullet$};
\node (2y) [] at (0,2)
   [label=left:{$c$}] {$\bullet$};
